A Collection of Thoughts on the Keccak/SHA-3 Construction

### 2018-04-25 s2018-math490/thesis/thesis.tex
Updates to thesis
Signed-off-by: Alexander Scheel <alexander.m.scheel@gmail.com>

@@

>>>>

For $w=1, 2$, we have verified that no fixed points occur which are valid blocks
for $1 \leq r \leq 24$, where $r$ is the number of rounds, at margins of 4 and
8 bits.

@@

For $w=1$, we reproduce a table of quantities of partial fixed points per round
below:
\begin{tabular}{c c c c c} \label{tab:f:p:1}
    Rounds & Quantity & Input & Output \\
    1 & 512 & & \\
    2 & 567 & & \\
    3 & 527 & & \\
    4 & 545 & & \\
    5 & 488 & & \\
    6 & 533 & & \\
    7 & 510 & & \\
\end{tabular}
Note that the above table is only for an effective margin of 256-bits (4 bits
when $w=1$). For an effective margin of 512-bits (8 bits), we found no such
partial fixed points. Further, example inputs and outputs are given as natural
numbers versus binary strings for compactness.

The following table describes our limits for finding partial fixed points
across various sizes of $w$, rounds, and whether or not we've been able to
complete an exhaustive search of all such instances.
\begin{tabular}{c c c c c} \label{tab:f:p:2}
    $w$ & Rounds & Exhaustive & Input & Output \\
\end{tabular}
